---
title: "Quarto example: `r params$project`"
author: "Vito"
format: 
  html:
    toc: true       # Table of Contents for easier navigation
    code-fold: true # Allows folding of code blocks for cleaner report view
    code-tools: true # Adds buttons to hide/show code
params:
  input_txt: '../results/test.txt'
  output_txt: '../results/test_copy.txt'
  project: 'Test'
  renv: NULL
---


# Introduction

Provide an introduction to your analysis here. You may include the purpose of the exploratory analysis, the dataset, and any specific questions you aim to address.

# Data Loading

```{r}
#| label: load-packages
#| message: false
# Load necessary libraries
library(tidyverse)
```

```{r}
#| label: load-data
data <- read_csv("../data/processed_data.csv")

# Display a summary of the dataset
summary(data)

# Check the structure of the dataset
str(data)

#| label: check-missing-values
# Count missing values in each column
data %>% summarise(across(everything(), ~ sum(is.na(.))))

#| label: visual-exploration
# Plot a histogram of a continuous variable (adjust for your dataset)
ggplot(data, aes(x = continuous_variable)) +
  geom_histogram(binwidth = 10, fill = "blue", color = "white") +
  labs(title = "Histogram of Continuous Variable", x = "Value", y = "Frequency")

#| label: scatterplot
# Example scatter plot between two continuous variables
ggplot(data, aes(x = variable_x, y = variable_y)) +
  geom_point() +
  labs(title = "Scatterplot of X vs Y", x = "X Variable", y = "Y Variable")



```

# Output

This section provides an analysis of xxx data. The purpose of this template is to provide an example of the data analysis output.

# Data Loading

```
library(dplyr)
library(gtsummary)
library(modelsummary)
library(estimatr)
library(ggplot2)
library(broom)
library(readr)

# Load your dataset (adjust the file path accordingly)
data <- read_csv("../data/health_insurance_data.csv")

str(data)

```


# Descriptive analysis

```
# Subset and select health insurance characteristics
insurance_data <- data %>%
  distinct(policy_id, .keep_all = TRUE) %>%
  select(gender, age_group, insurance_type, premium_paid)

# Summary statistics for health insurance data
insurance_summary <- insurance_data %>%
  tbl_summary(
    missing = "no",
    type = list(
      gender ~ "dichotomous",
      age_group ~ "categorical",
      insurance_type ~ "categorical"
    ),
    statistic = list(
      all_dichotomous() ~ "{p}%",
      all_categorical() ~ "{n} ({p}%)",
      premium_paid ~ "{mean} ({sd})"
    ),
    digits = list(
      all_dichotomous() ~ 1,
      all_categorical() ~ 1,
      premium_paid ~ 2
    ),
    label = list(
      gender ~ "Gender",
      age_group ~ "Age Group",
      insurance_type ~ "Insurance Type",
      premium_paid ~ "Premium Paid (in USD)"
    )
  ) %>%
  add_ci(include = everything(), pattern = "{stat} ({ci})") %>%
  modify_footnote(all_stat_cols() ~ "Notes: Proportion for categorical variables, mean (SD) for continuous variables.") 

# Display the summary table
insurance_summary

```

# t-test
```
# Conduct t-tests for premium_paid by insurance_type
t_test_results <- insurance_data %>%
  group_by(insurance_type) %>%
  summarise(
    t_test_premium = t.test(premium_paid ~ insurance_type)$p.value
  )

# Display t-test results
t_test_results
```

# Regression

```
# Fit a linear model (adjust variables as necessary)
model <- lm(premium_paid ~ gender + age_group + insurance_type, data = insurance_data)

# Summary of the regression model
summary(model)

# Display regression table with coefficients and significance
modelsummary(model, output = "markdown")
```
# Coefficients Plot
```
# Tidy the model for plotting
tidy_model <- broom::tidy(model)

# Plot the regression coefficients
ggplot(tidy_model, aes(x = estimate, y = term)) +
  geom_point() +
  geom_errorbarh(aes(xmin = estimate - std.error, xmax = estimate + std.error), height = 0.2) +
  labs(title = "Coefficient Plot", x = "Estimate", y = "Variable") +
  theme_minimal()
```